Rising Gun Violence in Toronto: An Analysis of Shootings and Firearm Discharges

### 2024-09-27 paper/paper.qmd
Changed

Shootings and gun discharges have become a growing concern in Toronto, but the public remains poorly informed about how specific factors such as time and place influence gun violence. The increase in gun-related incidents not only threatens public safety but also stresses policymakers, law enforcement, and local communities. Detailed analysis of data related to shooting incidents can show high-risk areas and times and provide solutions to reduce violence. In this paper, I analyze Toronto's reported shooting and gun discharge incidents between 2004 and 2024 and provide the public with relevant information in a brief, easy-to-read chart. We utilize “year”, “month” and “hour” variables to reveal trends in the number of victims over time and utilize latitude and longitude data to map the density of victims in order to determine which regions and time periods are at a higher risk of having a shooting incident.

@@

The rest of the paper is structured as follows: in @sec-data, we describe the source of the dataset and its context in detail. Next, we show our findings through various types of graphs with visualizations. After each chart, we discuss each graph's formation, the significance of the findings, and finally summarize key observations. Finally, there is an appendix and references. By the end of this paper, the reader will have a clearer understanding of trends in gun violence in Toronto and how this data can be utilized to improve safety measures throughout the city.

>>>>

Shootings and gun discharges have become a growing concern in Toronto, but the public still has an incomplete understanding of how specific factors, such as time and place, affect gun violence. The increase in gun-related incidents not only threatens public safety but also stresses policymakers, law enforcement, and local communities. Detailed analysis of data related to shooting incidents can show high-risk areas and times and provide solutions to reduce violence. In this paper, I analyze Toronto's reported shooting and gun discharge incidents between 2004 and 2024 and provide the public with relevant information in a brief, easy-to-read chart. We utilize “year”, “month” and “hour” variables to reveal trends in the number of victims over time and utilize latitude and longitude data to map the density of victims in order to determine which regions and time periods are at a higher risk of having a shooting incident.

@@

The rest of the paper is structured as follows: in @sec-data, we describe the source of the dataset and its context in detail. Next, we show our findings through various types of graphs with visualizations. After each chart, we discuss each graph's formation, the significance of the findings, and finally summarize key observations. Finally, there is an appendix and references.
